\section{Problem 1}

\begin{tabularx}{\textwidth}{|X|}
\hline
\textbf{Purpose}\\
To simplify complex statistical calculations with precise outcomes and enable users to gain valuable insights or analysis from the data\\\\
\textbf{Perspective}\\
Examine the use and results from the user's (data analysts, testers, developers) viewpoint\\\\
\textbf{Environment}\\
In the development and maintenance phase of the life cycle\\
\hline
\end{tabularx}

\begin{enumerate}
    \item \textbf{Question 1: How accurate are the results of METRICSTICS?}
    \begin{enumerate}
        \item{Metric 1: Compare the results with proven, benchmark calculations and calculate the percentage of the accuracy}
    \end{enumerate}
    
    \item \textbf{Question 2: Is the performance of METRICSTICS satisfactory from the users' viewpoint?}
    \begin{enumerate}
        \item{Metric 1: Measure computation time}
        \item{Metric 2: User surveys and feedback}
    \end{enumerate}
    
    \item \textbf{Question 3: Does METRICSTICS display results to a sufficient number of decimal places?}
    \begin{enumerate}
        \item{Metric 1: Measure the level of precision of the output}
        \item{Metric 2: User surveys and feedback}
    \end{enumerate}
    
    \item \textbf{Question 4: If an error occurs, are the messages intuitive and helpful enough to assist users to correct input mistakes?}
    \begin{enumerate}
        \item{Metric 1: User surveys and feedback}
    \end{enumerate}
    
    \item \textbf{Question 5: Can METRICSTICS handle large datasets as inputs?}
    \begin{enumerate}
        \item{Metric 1: Measure and analyze the capability to handle large datasets}
    \end{enumerate}
    
    \item \textbf{Question 6: Can the users of METRICSTICS use it autonomously?}
    \begin{enumerate}
        \item{Metric 1: User surveys and feedback}
        \item{Metric 2: Evaluate the quality and accessibility of user documentation, tutorials, training and help resources}
    \end{enumerate}
    
    \item \textbf{Question 7: Does METRICSTICS provide sufficient functionalities?}
    \begin{enumerate}
        \item{Metric 1: Compare functionality available between METRICSTICS and those commonly used functionalities in research and data analysis}
    \end{enumerate}
    
    \item \textbf{Question 8: Can METRICSTICS be used across different platforms (e.g. Windows, macOS, iOS, Android)?}
    \begin{enumerate}
        \item{Metric 1: Evaluate compatibility across various platforms}
    \end{enumerate}
    
    \item \textbf{Question 9: How long does it take a user to complete a task using METRICSTICS?}
    \begin{enumerate}
        \item{Metric 1: Measure the time required and calculate the average time taken}
    \end{enumerate}
    
    \item \textbf{Question 10: Is the user interface and the overall experience of METRICSTICS easy to use?}
    \begin{enumerate}
        \item{Metric 1: User surveys and feedback}
        \item{Metric 2: Compare time-based efficiency between a new user and a returning user}
    \end{enumerate}

\end{enumerate}

\pagebreak
